### 2023-04-08 resources/exposure.tex
manuscript prepared
fixed interventions; BS

% Created by tikzDevice version 0.12.3.1 on 2022-04-22 17:18:12
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 25.15, 28.21) rectangle (155.80,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.15, 28.21) rectangle (155.80,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15, 56.10) --
	(155.80, 56.10);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,101.47) --
	(155.80,101.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 25.15,146.83) --
	(155.80,146.83);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.63, 28.21) --
	( 48.63,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 75.63, 28.21) --
	( 75.63,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (102.62, 28.21) --
	(102.62,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.62, 28.21) --
	(129.62,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 33.42) --
	(155.80, 33.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15, 78.78) --
	(155.80, 78.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 25.15,124.15) --
	(155.80,124.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14, 28.21) --
	( 35.14,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.13, 28.21) --
	( 62.13,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.13, 28.21) --
	( 89.13,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.12, 28.21) --
	(116.12,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.12, 28.21) --
	(143.12,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14,116.20) --
	( 36.49,154.33) --
	( 37.83,144.98) --
	( 39.18,118.42) --
	( 40.53,121.74) --
	( 41.88,121.74) --
	( 43.23,122.07) --
	( 44.58,133.91) --
	( 45.93,153.22) --
	( 47.28,154.33) --
	( 48.63,154.33) --
	( 49.98,156.14) --
	( 51.33,154.33) --
	( 52.68,133.91) --
	( 54.03,154.33) --
	( 55.38,156.14) --
	( 56.73,156.14) --
	( 58.08,156.14) --
	( 59.43,133.91) --
	( 60.78,154.33) --
	( 62.13,145.58) --
	( 63.48,141.88) --
	( 64.83,120.02) --
	( 66.18,133.91) --
	( 67.53,134.46) --
	( 68.88,122.01) --
	( 70.23, 94.47) --
	( 71.58,103.66) --
	( 72.93, 95.01) --
	( 74.28, 94.47) --
	( 75.63, 92.26) --
	( 76.98, 92.10) --
	( 78.33, 83.33) --
	( 79.68, 83.33) --
	( 81.03, 85.43) --
	( 82.38, 85.43) --
	( 83.73, 83.33) --
	( 85.08, 85.43) --
	( 86.43, 80.26) --
	( 87.78, 83.77) --
	( 89.13, 87.97) --
	( 90.48, 84.75) --
	( 91.83, 90.01) --
	( 93.18, 90.64) --
	( 94.53, 87.88) --
	( 95.87, 86.46) --
	( 97.22, 85.35) --
	( 98.57, 83.33) --
	( 99.92, 83.33) --
	(101.27, 85.19) --
	(102.62, 52.02) --
	(103.97, 52.30) --
	(105.32, 50.60) --
	(106.67, 50.94) --
	(108.02, 47.63) --
	(109.37, 48.18) --
	(110.72, 49.42) --
	(112.07, 49.79) --
	(113.42, 49.46) --
	(114.77, 49.79) --
	(116.12, 44.84) --
	(117.47, 46.82) --
	(118.82, 43.96) --
	(120.17, 44.33) --
	(121.52, 48.46) --
	(122.87, 46.75) --
	(124.22, 44.89) --
	(125.57, 44.67) --
	(126.92, 43.52) --
	(128.27, 43.38) --
	(129.62, 43.35) --
	(130.97, 42.97) --
	(132.32, 42.70) --
	(133.67, 41.95) --
	(135.02, 39.09);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 25.15, 28.21) rectangle (155.80,162.23);
\end{scope}
\begin{scope}
\path[clip] (161.30, 28.21) rectangle (291.96,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (161.30, 28.21) rectangle (291.96,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30, 56.10) --
	(291.96, 56.10);

\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30,101.47) --
	(291.96,101.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] (161.30,146.83) --
	(291.96,146.83);

\path[draw=drawColor,line width= 0.3pt,line join=round] (184.79, 28.21) --
	(184.79,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (211.79, 28.21) --
	(211.79,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (238.78, 28.21) --
	(238.78,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (265.78, 28.21) --
	(265.78,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30, 33.42) --
	(291.96, 33.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30, 78.78) --
	(291.96, 78.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.30,124.15) --
	(291.96,124.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] (171.29, 28.21) --
	(171.29,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.29, 28.21) --
	(198.29,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.28, 28.21) --
	(225.28,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.28, 28.21) --
	(252.28,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (279.27, 28.21) --
	(279.27,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (171.29, 38.43) --
	(172.64, 41.00) --
	(173.99, 44.55) --
	(175.34, 41.44) --
	(176.69, 41.41) --
	(178.04, 43.59) --
	(179.39, 39.58) --
	(180.74, 45.48) --
	(182.09, 46.31) --
	(183.44, 48.44) --
	(184.79, 44.69) --
	(186.14, 48.44) --
	(187.49, 48.44) --
	(188.84, 40.74) --
	(190.19, 43.24) --
	(191.54, 44.57) --
	(192.89, 44.87) --
	(194.24, 48.44) --
	(195.59, 39.48) --
	(196.94, 48.44) --
	(198.29, 42.04) --
	(199.64, 51.78) --
	(200.99, 48.44) --
	(202.34, 51.09) --
	(203.69, 51.78) --
	(205.04, 47.41) --
	(206.39, 54.88) --
	(207.74, 57.99) --
	(209.09, 52.89) --
	(210.44, 53.09) --
	(211.79, 51.22) --
	(213.14, 43.75) --
	(214.49, 39.34) --
	(215.84, 38.74) --
	(217.19, 39.51) --
	(218.53, 39.79) --
	(219.88, 39.48) --
	(221.23, 39.48) --
	(222.58, 38.45) --
	(223.93, 40.70) --
	(225.28, 40.77) --
	(226.63, 39.48) --
	(227.98, 43.17) --
	(229.33, 43.78) --
	(230.68, 43.24) --
	(232.03, 43.81) --
	(233.38, 43.81) --
	(234.73, 43.81) --
	(236.08, 43.81) --
	(237.43, 43.81) --
	(238.78, 39.57) --
	(240.13, 40.14) --
	(241.48, 40.57) --
	(242.83, 39.42) --
	(244.18, 37.52) --
	(245.53, 37.52) --
	(246.88, 36.98) --
	(248.23, 36.49) --
	(249.58, 36.49) --
	(250.93, 36.49) --
	(252.28, 36.49) --
	(253.63, 36.49) --
	(254.98, 36.07) --
	(256.33, 36.38) --
	(257.68, 36.49) --
	(259.03, 36.49) --
	(260.38, 37.34) --
	(261.73, 37.85) --
	(263.08, 37.83) --
	(264.43, 37.00) --
	(265.78, 37.55) --
	(267.13, 37.79) --
	(268.48, 37.52) --
	(269.83, 37.68) --
	(271.18, 36.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (161.30, 28.21) rectangle (291.96,162.23);
\end{scope}
\begin{scope}
\path[clip] (297.46, 28.21) rectangle (428.12,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (297.46, 28.21) rectangle (428.12,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46, 56.10) --
	(428.12, 56.10);

\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46,101.47) --
	(428.12,101.47);

\path[draw=drawColor,line width= 0.3pt,line join=round] (297.46,146.83) --
	(428.12,146.83);

\path[draw=drawColor,line width= 0.3pt,line join=round] (320.95, 28.21) --
	(320.95,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (347.94, 28.21) --
	(347.94,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (374.94, 28.21) --
	(374.94,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (401.93, 28.21) --
	(401.93,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46, 33.42) --
	(428.12, 33.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46, 78.78) --
	(428.12, 78.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.46,124.15) --
	(428.12,124.15);

\path[draw=drawColor,line width= 0.6pt,line join=round] (307.45, 28.21) --
	(307.45,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (334.45, 28.21) --
	(334.45,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.44, 28.21) --
	(361.44,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (388.44, 28.21) --
	(388.44,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (415.43, 28.21) --
	(415.43,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (308.80, 44.87) --
	(310.15, 44.87) --
	(311.50, 44.87) --
	(312.85, 42.13) --
	(314.20, 42.13) --
	(315.55, 44.87) --
	(316.90, 44.87) --
	(318.25, 44.27) --
	(319.60, 42.32) --
	(320.95, 48.60) --
	(322.30, 50.46) --
	(323.65, 69.90) --
	(325.00, 69.90) --
	(326.35, 69.90) --
	(327.70, 42.93) --
	(329.05, 42.93) --
	(330.40, 50.03) --
	(331.75,116.91) --
	(333.10,120.23) --
	(334.45, 42.93) --
	(335.80, 42.93) --
	(337.15, 64.53) --
	(338.50, 76.72) --
	(339.85, 64.53) --
	(341.19, 53.70) --
	(342.54, 64.53) --
	(343.89, 53.70) --
	(345.24, 43.76) --
	(346.59, 43.30) --
	(347.94, 40.78) --
	(349.29, 50.31) --
	(350.64, 51.13) --
	(351.99, 38.87) --
	(353.34, 38.87) --
	(354.69, 39.55) --
	(356.04, 38.90) --
	(357.39, 40.47) --
	(358.74, 38.87) --
	(360.09, 38.87) --
	(361.44, 38.93) --
	(362.79, 38.87) --
	(364.14, 38.87) --
	(365.49, 38.88) --
	(366.84, 39.40) --
	(368.19, 40.34) --
	(369.54, 39.02) --
	(370.89, 40.49) --
	(372.24, 40.05) --
	(373.59, 41.08) --
	(374.94, 35.04) --
	(376.29, 35.19) --
	(377.64, 35.19) --
	(378.99, 35.03) --
	(380.34, 34.30) --
	(381.69, 34.31) --
	(383.04, 34.53) --
	(384.39, 34.50) --
	(385.74, 34.43) --
	(387.09, 34.76) --
	(388.44, 34.80) --
	(389.79, 34.95) --
	(391.14, 34.71) --
	(392.49, 34.93) --
	(393.84, 35.19) --
	(395.19, 35.19) --
	(396.54, 36.02) --
	(397.89, 36.03) --
	(399.23, 36.02) --
	(400.58, 35.81) --
	(401.93, 36.04) --
	(403.28, 35.88) --
	(404.63, 35.23) --
	(405.98, 36.84) --
	(407.33, 35.58);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.46, 28.21) rectangle (428.12,162.23);
\end{scope}
\begin{scope}
\path[clip] ( 25.15,162.23) rectangle (155.80,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 25.15,162.23) rectangle (155.80,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 90.48,165.60) {Soluble};
\end{scope}
\begin{scope}
\path[clip] (161.30,162.23) rectangle (291.96,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (161.30,162.23) rectangle (291.96,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (226.63,165.60) {Straight};
\end{scope}
\begin{scope}
\path[clip] (297.46,162.23) rectangle (428.12,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (297.46,162.23) rectangle (428.12,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (362.79,165.60) {Synthetic};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.14, 25.46) --
	( 35.14, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.13, 25.46) --
	( 62.13, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.13, 25.46) --
	( 89.13, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.12, 25.46) --
	(116.12, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.12, 25.46) --
	(143.12, 28.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 35.14, 17.75) {1920};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 62.13, 17.75) {1940};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 89.13, 17.75) {1960};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (116.12, 17.75) {1980};

>>>>

% Created by tikzDevice version 0.12.3.1 on 2023-04-06 10:31:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 35.37, 28.21) rectangle (162.62,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 35.37, 28.21) rectangle (162.62,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 44.76) --
	(162.62, 44.76);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 69.57) --
	(162.62, 69.57);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37, 94.37) --
	(162.62, 94.37);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,119.17) --
	(162.62,119.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 35.37,143.98) --
	(162.62,143.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.54, 28.21) --
	( 63.54,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (100.86, 28.21) --
	(100.86,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (138.18, 28.21) --
	(138.18,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 32.36) --
	(162.62, 32.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 57.16) --
	(162.62, 57.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37, 81.97) --
	(162.62, 81.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,106.77) --
	(162.62,106.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,131.58) --
	(162.62,131.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.37,156.38) --
	(162.62,156.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.88, 28.21) --
	( 44.88,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.20, 28.21) --
	( 82.20,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.52, 28.21) --
	(119.52,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.83, 28.21) --
	(156.83,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.75,139.99) --
	( 48.61,123.33) --
	( 50.48,130.79) --
	( 52.35,140.45) --
	( 54.21,128.18) --
	( 56.08,130.82) --
	( 57.94,143.76) --
	( 59.81,143.17) --
	( 61.68,156.14) --
	( 63.54,142.11) --
	( 65.41,141.53) --
	( 67.27,118.13) --
	( 69.14,127.52) --
	( 71.00,133.98) --
	( 72.87,137.54) --
	( 74.74,132.30) --
	( 76.60,138.56) --
	( 78.47,120.48) --
	( 80.33,141.46) --
	( 82.20,145.32) --
	( 84.07,141.53) --
	( 85.93,149.94) --
	( 87.80,150.14) --
	( 89.66,146.20) --
	( 91.53,141.53) --
	( 93.39,141.53) --
	( 95.26,141.53) --
	( 97.13,141.53) --
	( 98.99,142.55) --
	(100.86, 71.73) --
	(102.72, 72.60) --
	(104.59, 69.29) --
	(106.46, 69.92) --
	(108.32, 62.24) --
	(110.19, 63.56) --
	(112.05, 66.32) --
	(113.92, 68.18) --
	(115.78, 66.95) --
	(117.65, 68.18) --
	(119.52, 57.01) --
	(121.38, 61.53) --
	(123.25, 55.24) --
	(125.11, 55.83) --
	(126.98, 65.33) --
	(128.85, 61.53) --
	(130.71, 57.67) --
	(132.58, 56.97) --
	(134.44, 54.48) --
	(136.31, 54.14) --
	(138.18, 54.08) --
	(140.04, 53.17) --
	(141.91, 52.60) --
	(143.77, 50.78) --
	(145.64, 44.72);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 35.37, 28.21) rectangle (162.62,162.23);
\end{scope}
\begin{scope}
\path[clip] (168.12, 28.21) rectangle (295.37,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.12, 28.21) rectangle (295.37,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12, 44.76) --
	(295.37, 44.76);

\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12, 69.57) --
	(295.37, 69.57);

\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12, 94.37) --
	(295.37, 94.37);

\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12,119.17) --
	(295.37,119.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] (168.12,143.98) --
	(295.37,143.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] (196.29, 28.21) --
	(196.29,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (233.61, 28.21) --
	(233.61,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (270.93, 28.21) --
	(270.93,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12, 32.36) --
	(295.37, 32.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12, 57.16) --
	(295.37, 57.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12, 81.97) --
	(295.37, 81.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12,106.77) --
	(295.37,106.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12,131.58) --
	(295.37,131.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (168.12,156.38) --
	(295.37,156.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (177.63, 28.21) --
	(177.63,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.95, 28.21) --
	(214.95,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.27, 28.21) --
	(252.27,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (289.58, 28.21) --
	(289.58,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (179.50, 64.49) --
	(181.37, 67.76) --
	(183.23, 54.42) --
	(185.10, 58.48) --
	(186.96, 50.99) --
	(188.83, 54.60) --
	(190.69, 56.67) --
	(192.56, 51.09) --
	(194.43, 53.62) --
	(196.29, 45.62) --
	(198.16, 43.01) --
	(200.02, 43.01) --
	(201.89, 43.37) --
	(203.76, 43.37) --
	(205.62, 43.37) --
	(207.49, 43.37) --
	(209.35, 43.37) --
	(211.22, 43.37) --
	(213.08, 43.37) --
	(214.95, 44.40) --
	(216.82, 43.37) --
	(218.68, 46.38) --
	(220.55, 45.62) --
	(222.41, 48.79) --
	(224.28, 54.13) --
	(226.15, 55.09) --
	(228.01, 55.09) --
	(229.88, 55.09) --
	(231.74, 55.09) --
	(233.61, 45.48) --
	(235.48, 46.84) --
	(237.34, 48.19) --
	(239.21, 45.83) --
	(241.07, 41.35) --
	(242.94, 41.35) --
	(244.80, 39.86) --
	(246.67, 39.08) --
	(248.54, 39.08) --
	(250.40, 39.08) --
	(252.27, 39.08) --
	(254.13, 39.08) --
	(256.00, 38.03) --
	(257.87, 38.83) --
	(259.73, 39.08) --
	(261.60, 39.08) --
	(263.46, 40.81) --
	(265.33, 42.05) --
	(267.19, 42.01) --
	(269.06, 39.65) --
	(270.93, 41.22) --
	(272.79, 41.91) --
	(274.66, 41.29) --
	(276.52, 41.67) --
	(278.39, 39.78);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.12, 28.21) rectangle (295.37,162.23);
\end{scope}
\begin{scope}
\path[clip] (300.87, 28.21) rectangle (428.12,162.23);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (300.87, 28.21) rectangle (428.12,162.23);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87, 44.76) --
	(428.12, 44.76);

\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87, 69.57) --
	(428.12, 69.57);

\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87, 94.37) --
	(428.12, 94.37);

\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87,119.17) --
	(428.12,119.17);

\path[draw=drawColor,line width= 0.3pt,line join=round] (300.87,143.98) --
	(428.12,143.98);

\path[draw=drawColor,line width= 0.3pt,line join=round] (329.04, 28.21) --
	(329.04,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (366.36, 28.21) --
	(366.36,162.23);

\path[draw=drawColor,line width= 0.3pt,line join=round] (403.68, 28.21) --
	(403.68,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87, 32.36) --
	(428.12, 32.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87, 57.16) --
	(428.12, 57.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87, 81.97) --
	(428.12, 81.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87,106.77) --
	(428.12,106.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87,131.58) --
	(428.12,131.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (300.87,156.38) --
	(428.12,156.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.38, 28.21) --
	(310.38,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (347.70, 28.21) --
	(347.70,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (385.02, 28.21) --
	(385.02,162.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (422.34, 28.21) --
	(422.34,162.23);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (312.25, 72.54) --
	(314.12,127.07) --
	(315.98,127.07) --
	(317.85,113.74) --
	(319.71, 88.56) --
	(321.58,100.41) --
	(323.45, 76.72) --
	(325.31, 54.98) --
	(327.18, 53.98) --
	(329.04, 48.46) --
	(330.91, 70.36) --
	(332.77, 71.10) --
	(334.64, 44.28) --
	(336.51, 44.28) --
	(338.37, 45.88) --
	(340.24, 44.35) --
	(342.10, 48.14) --
	(343.97, 44.28) --
	(345.84, 44.28) --
	(347.70, 44.97) --
	(349.57, 44.28) --
	(351.43, 44.28) --
	(353.30, 44.40) --
	(355.17, 45.60) --
	(357.03, 47.66) --
	(358.90, 45.21) --
	(360.76, 48.23) --
	(362.63, 47.55) --
	(364.49, 50.24) --
	(366.36, 35.96) --
	(368.23, 36.25) --
	(370.09, 36.25) --
	(371.96, 35.89) --
	(373.82, 34.30) --
	(375.69, 34.30) --
	(377.56, 34.62) --
	(379.42, 34.66) --
	(381.29, 34.45) --
	(383.15, 35.26) --
	(385.02, 35.37) --
	(386.88, 35.70) --
	(388.75, 35.18) --
	(390.62, 35.67) --
	(392.48, 36.25) --
	(394.35, 36.25) --
	(396.21, 38.05) --
	(398.08, 38.07) --
	(399.95, 38.05) --
	(401.81, 37.68) --
	(403.68, 38.10) --
	(405.54, 37.67) --
	(407.41, 36.10) --
	(409.27, 39.85) --
	(411.14, 37.05);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.87, 28.21) rectangle (428.12,162.23);
\end{scope}
\begin{scope}
\path[clip] ( 35.37,162.23) rectangle (162.62,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 35.37,162.23) rectangle (162.62,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 98.99,165.60) {Soluble};
\end{scope}
\begin{scope}
\path[clip] (168.12,162.23) rectangle (295.37,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (168.12,162.23) rectangle (295.37,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (231.74,165.60) {Straight};
\end{scope}
\begin{scope}
\path[clip] (300.87,162.23) rectangle (428.12,175.17);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (300.87,162.23) rectangle (428.12,175.17);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (364.49,165.60) {Synthetic};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 44.88, 25.46) --
	( 44.88, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.20, 25.46) --
	( 82.20, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (119.52, 25.46) --
	(119.52, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (156.83, 25.46) --
	(156.83, 28.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 44.88, 17.75) {1940};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 82.20, 17.75) {1960};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (119.52, 17.75) {1980};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (156.83, 17.75) {2000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (177.63, 25.46) --
	(177.63, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.95, 25.46) --
	(214.95, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.27, 25.46) --
	(252.27, 28.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (289.58, 25.46) --
	(289.58, 28.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (177.63, 17.75) {1940};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (214.95, 17.75) {1960};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (252.27, 17.75) {1980};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (289.58, 17.75) {2000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,180.67);
\definecolor{drawColor}{gray}{0.20}
